Deep learning on psychological arousal classification

### 2015-05-07 paper/paper.tex
some stuff in data

\section{Data} \label{section:data}
%TODO: we have big data, oooh. okay maybe not that big but it still takes forever to load 
%-Dataset (details)
% -processing
%-Features
% -raw
% -dtft
%  -windows
% -wavelets
% -other

>>>>

\section{Data} \label{section:data}
Our experiment uses data from Siegle et al. (forthcoming). To our knowledge, this is the largest dataset of EEG collected in controlled laboratory conditions (TODO: get x and n) with n unique subjects from x different sites. The dataset contains various stimuli types and our experiments focus on the IAPS stimuli (TODO: cite lang et al 2008). IAPS is a set of images designed to illicit emotional responses along two emotional axes - high, low arousal and positive, negative valence. The stimuli
fall into 4 categories - low arousal positive valence, low arousal negative valence, high arousal positive valence, and high arousal negative valence. In this dataset, each subject viewed 10 images from each category with a 2 (TODO: check this) second fixation period between each stimulus category. One limitation of the experiment was that the images were shown to the subject in the same sequence.

The data was processed with %TODO: asdfasdfasdf how did siegle process the data??
%TODO: we have big data, oooh. okay maybe not that big but it still takes forever to load 
%-Dataset (details)
% -processing
%-Features
% -raw
% -dtft
%  -windows
% -wavelets
% -other
